### 2021-07-20 homework/hmwks/hmwk1.tex
fixed unnecessary thingy

For a \colorbox{REDE}{time-independent} Hamiltonian $\hat{H}$, the state of the system at time $t$ is given by the solution to the Schr{\"o}dinger equation $\displaystyle i\hbar \frac{d \ket{\psi(t)}}{dt} = \hat{H} \ket{\psi(t)}$:

>>>>

For a time-independent Hamiltonian $\hat{H}$, the state of the system at time $t$ is given by the solution to the Schr{\"o}dinger equation $\displaystyle i\hbar \frac{d \ket{\psi(t)}}{dt} = \hat{H} \ket{\psi(t)}$:
